Generating Simulated Data

### 2021-05-13 docs/SimData.Rmd
daily stomach weight attempt 1, looks wrong

What we have saved so far is a diet comp in proportion that has had bias and observation error added to proportions. However, we need the stomach weight portion of the equation, which has the survey timing/area/efficiency/selectivity applied to true consumed weight.

@@

@@

  # get numbers at ageclass for same survey design
  survey_N <- atlantisom::create_survey(dat = omlist_ss$truenums_ss,
                                        time = survtime,
                                        species = survspp,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex.agecl)

  # divide surv_cons by survey numbers at agecl to get per capita consumption at agecl

>>>>

What we have saved so far is a diet comp in proportion that has had bias and observation error added to proportions. However, we need the stomach weight portion of the equation, which has the survey timing/area/efficiency/selectivity applied to true consumed weight. The hydra input is mean daily stomach weight in grams. From the Atlantis manual, "DetailedDietCheck.txt returns the total consumed biomass since the last output given for each cell (box and layer) of each age group of each functional group." So daily per capita consumed biomass is this output, summed over prey for total consumption, divided by the numbers from the same survey design, divided by the output step `omlist_ss$runpar$outputstep`.

@@

omlist_ss <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

source(here("simulated-data/config/omdimensions.R"))

@@

  # get numbers at ageclass for same survey design
  # note different time units!
  survey_N <- atlantisom::create_survey(dat = omlist_ss$truenums_ss,
                                        time = survey_sample_full,
                                        species = survspp,
                                        boxes = survboxes,
                                        effic = surveffic,
                                        selex = survselex.agecl)

  # convert survey N times to cons times in days
  survey_N$time <- survey_N$time*omlist_ss$runpar$outputstep

  survey_totN <- survey_N %>%
    group_by(species, agecl, time) %>%
    summarise(totN = sum(atoutput)) %>%
    ungroup()

  # sum over prey to get total consumption in t, divide by N and timestep, convert to g
  survey_totcons <- survey_cons %>%
    group_by(species, agecl, time) %>%
    summarise(totcons = sum(atoutput)) %>%
    ungroup() %>%
    left_join(survey_totN) %>%
    mutate(percap_cons = totcons/totN) %>%
    mutate(daily_percap_g = percap_cons/omlist_ss$runpar$outputstep*1000000)
